Change in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2019-12-05 analysis/paper/paper.Rmd
the three paragraphs done

<!-- this is what I'm newly writing 
In this research, we try to answer the three questions to understand the technological transition period. First, we are asking how the introduction of the new tools changed the usage of landscape. The new technology might allow hunter-gatherers to explore and stay in different or harsher territories by increasing mobility as well as innovating hunting strategies []. Or people could change their landscape using the new tools such as []. 
According to ethnographic observations of mobility, people move frequently with little knowledge of the places for foraging and acquiring raw materials purpose with portable, mulifunctional, long lasting tools[@clarkson2008lithics;@kuhn2014mousterian]. The study reported here was designed to

Second, we focus on how did the new technology change the way people use their sites whether they tended to stay in one spot longer as a base campe or shorter period for specific purpose such as summer hunting camp. The stone artifact assemblage from a site can inform us how long individuals or groupd stayed or what they did there so we can assume the way people use the site. It is because a stone artifact
contains a record of material transport and selection and it was carefully designed so that people could make a living from the landscape that constraints the production, efficiency, use, transportation, and maintenance [@clarkson2008lithics]. This project will look into stone assemblages that hunter-gatherers left behind to understand the site occupation pattern change during the transition period and the relationship with the appearance of new tools.

@@

@@

- Site is a place where past activity is preserved with material evidence.

>>>>

In this research, we try to answer the three questions to understand the technological transition period. First, we are asking how the introduction of the new tools related to the usage of landscape. The new technology might allow hunter-gatherers to explore and stay in different or harsher territories by increasing mobility as well as innovating foraging strategies. In addition, the new tool production technique required hunter-gatherers to move for acquiring specific raw materials [@blumenschine2008effects; @reti2016quantifying]. According to ethnographic observations of mobility, people move frequently with little knowledge of the places for foraging and acquiring raw materials purpose with portable, mulifunctional, long lasting tools[@clarkson2008lithics;@kuhn2014mousterian]. The study reported here was designed to interpret the impact of the new tools on the landscape use during the transitional period.

<!-- I think we were also talking about example that a new tech actually changed the landscape. But I'm not sure where I can put the example

For example, the new technology could change their landscape. Hominin fire use in the early Pleistocene has been studied and some argue that usage of fire changed the landscape and their dietary [@pruetz2010brief; @glikson2013fire; @parker2016pyrophilic; @hlubik2019hominin].

Second, we focus on how the new technology changed the way people use their sites whether they tended to stay in one spot longer as a base campe or shorter period for specific purpose such as summer hunting camp. The stone artifact assemblage from a site can inform us how long individuals or groupd stayed or what they did there so we can assume the way people use the site [@binford1979organization; @kelly1995foraging; @kuhn2016moves; @holdaway2019surface]. Stone artifact contains a record of material transport and selection because it was carefully designed so that people could make a living from the landscape that constraints the production, efficiency, use, transportation, and maintenance [@clarkson2008lithics]. Archaeological sites indicate depositional phenomena and places where artifacts and other debris accumulated reflecting human activities in the past [@kuhn2015artifact]. This project will look into stone assemblages that hunter-gatherers left behind to understand the site occupation pattern change during the transition period and the relationship with the appearance of new tools.

@@

-------------- previous paragraphs ------

@@

- Site is a place where past activity is preserved with material evidence (GP).

- What we call sites are essentially depositional phenomena, places where, for behavioral or geologic reasons, artifacts and other debris accumulated in sufficient concentrations to attract the attention of archeologists (Kuhn and Clark 2015).

==> I put "Archaeological sites indicate depositional phenomena and places where artifacts and other debris accumulated reflecting human activities in the past" in the paragraph of the second question.
